Safe and Robust Formal Synthesis of Digital Controllers\\ for Continuous Plants

### 2018-04-03 automatica/paper.tex
added additional benchmarks to the table
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

>>>>

We provide the results in Table~\ref{tab:results}.  Here 
\textit{Benchmark} is the name of the respective benchmark, 
\textit{Order} is the number of continuous variables, 
$\mathcal{F}_{\langle I_p,F_p \rangle}$ and $\mathcal{F}_{\langle p \rangle}$  
are the fixed- and floating-point precision used to model the plant, respectively;
while \textit{Time} is the total time required to synthesize a controller for the given
plant with one of the two methods.  Timeouts are indicated by~\xmark.  The
precision for the controller, $\mathcal{F}_{\langle I_c,F_c \rangle}$, is
chosen to be $I_c = 8$, $F_c = 8$ for fixed-point and 
$\mathcal{F}_{\langle p \rangle}$ is chosen to be half-precision for floating-point.

\begin{table*}
\centering
\begin{tabular}{| r | l | c | c | r | c | r | c | r | c | r |}
%
\hline
\# & \multicolumn{1}{|c|}{Benchmark} & \multicolumn{1}{|c|}{Order} & \multicolumn{4}{|c|}{Multi-staged}                 & \multicolumn{4}{|c|}{Abstraction} \\
   &                                  & & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle I_p,F_p \rangle}$} & \multicolumn{1}{|c|}{Time} & \multicolumn{1}{|c|}{$\mathcal{F}_{\langle p \rangle}$} & \multicolumn{1}{|c|}{Time}\\\hline
1  & Cruise Control  & 1 &   &  &  &  & & & &\\
2  & DC Motor          & 2 &   &  &  &  & & & &\\
3  & Helicopter        & 3 &  &   &  &  & & & &\\
4  & Inverted Pendulum & 4 &   &  &  & & & & &\\
5  & Magnetic Pointer  & 2 & &  &  &  & & & &\\
6  & Magnetic Suspension & 2 &  & & & & & & &\\
7  & Pendulum          & 2 &   & & & & & & &\\
8  & Suspension        & 2 &  & & & & & & &\\
9  & Tape Driver       & 3 &   & & & & & & &\\
10 & Satellite          & 2 &   &  & & & & & &\\
12 & Voltage Regulator & &   &  & & & & & &\\
13 & Guidance Control  & &   &  & & & & & &\\
14 & Spring Mass   & &   &  & & & & & &\\
\hline
%
\end{tabular}
\vspace{0.05in}
\caption{Experimental results\label{tab:results}}
\end{table*}
